%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman
\usepackage[utf8]{inputenc}
\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{courier}
\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Zhijian} % Your first name
\familyname{Wen} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{Unit 304, 20 Upper Queen Street}{Auckland}
\mobile{021-0799395}


\email{zhijianwen1992@gmail.com}
% \homepage{alannungaray.com.mx/}{alannungaray.com.mx} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
% \extrainfo{https://www.facebook.com/AlanDNungaray}
% \photo[60pt][0.4pt]{pictures/foto} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Personal Summary}
I am a graduate with Master major in Statistics, with experiences in data analysis/modelling, programming including developing \textbf{R}-package and data mining. I am interesting in programming and I am enjoying to ``talk'' with computer. I am keen to join your company where I want to  utilize my skills in creative. \\

\section{Education}
\cventry{2016--Present}{Msc - Statistics}{University of Auckland}{}{}{
	\textit{Key course: Multivariate Analysis, Data Science Practice, Statistical Inference} \\
}
	
\cventry{2015--2016}{BSc(Hons) - Statistics}{University of Auckland}{}{}{
	\textit{Key course: Bayesian Inference, Statistical Computing, Statistical Modelling}\\
	\textit{class representation of \textbf{Stats 779} } \\
}
\cventry{2012--2015}{BSc - Mathematics and Statistics}{University of Auckland}{}{}{~\\}

\section{Projects}
\cventry{Master}{Emulate the \texttt{persp} plot and \texttt{filled.contour} plot in \texttt{gridGraphics}}{}{}{}{
		\textit{The \texttt{persp()} is use for drawing 3-D surface and the \texttt{filled.contour()} is use for drawing filled level contour plot in the \textbf{graphics} package, which is the based package in \textbf{R}. My job is to convert(redraw) these two kinds of plot(functions) to \textbf{grid}}.\\
		\textit{Supervisor: Associate Professor Paul Murrell} \\
}

\cventry{Honours}{Bayesian inference on forensic glass evidence}{}{}{}{
		\textit{The aim of this project is to fit a zero inflated poisson mixture model and zero inflated negative mixture model to different situations (e.g. The breaker's distance from the window, Proportion of high persistence fragments)}. \\
		\textit{Supervisor: Professor James Curran} \\
}

\newpage
\section{Work Experience}
% Arguments not required can be left empty
\cventry{2016-2017}{Teaching assistant}  {}{}{}{
	~\\
	\textbf{Tutor and Marker of Stats 220}: This course introduces a variety of computer technologies relevant to storing, managing, and processing data. My job is to help students to understand and solve the questions about the coding. Such as \texttt{HTML/CSS}, \texttt{SQL} and \texttt{R} \\~\\
	\textbf{Marker of Stats 380}: A course of statistical computing using the \texttt{R} statistical computing environment\\}

\cventry{2015-2016}{Summer Scholarship}  {}{Working on the iNZightMaps package, used in the mapping module for iNZight}{}{}
%------------------------------------------------
%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}

\cvitem{Advance:}{\textsc{R}, \textsc{HTML}, \LaTeX} 
\cvitem{Fair:}{SAS, SQL,jags, Linux, Lua, JavaScript}
\cvitem{Basic:}{C, C++, JAON, XML, \textsc{Matlab}, Excel}


%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}
\cvitemwithcomment{}{English, Mandarin, Cantonese}{}

\section{Interest}
\cvlistdoubleitem{Game Computing}{Statistical Computing}
\cvlistdoubleitem{Table tennis}{Physics}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------




%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

\clearpage

\recipient{HR}{Blue Trail Software\\Niños Heroes 115\\47600 Tepatitlán de Morelos, Jalisco} % Letter recipient
\date{\today} % Letter date
\opening{Estimated BTS} % Opening greeting
\closing{.} % Closing phrase
\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title
I am writing this letter to express my desire to work and innovate for you, for the world.

I enjoying on programming. Since my first year at University, I starting learning some programming language such as html/css, Matlab. During the Bachelor Degree of my university life, I learned html, xml, latex, matlab and R. R is one of my favorite programming language therefore I starting doing my Honours and Master degree to learn deeper about R.\\

During the summer of 2016, I was doing the summer scholarship which working on the \texttt{iNZightMaps} package which used for the mapping module for iNZight. I leaned a lot of graphics on R, specially the high-level graphics - the \texttt{grid} package. \\

Although I am a statistic student, I coding a lots and I used R to help me to analysis data to defeat any assignments and projects.
I started my master dissertation with my supervisor, Dr.Paul Merrel who is a member of R core team, and now I still working on my dissertation.\\

Talking with computer is interesting. Although I'm not a front-line of programmer, I would like to use my coding experience to solve messy problem, and also willing to learn any other computing language in the future.\\

\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}